Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-03-10 ms.tex
infrared

Although the present analysis constituted a significant data processing 
endeavor, it represents only a small fraction of the work that must
be done to maximize science return from the NEOWISER imaging data set.
Creation of time-resolved coadds spanning the $\sim$5 year AllWISE-NEOWISER
time baseline would enable a wealth of important time-domain projects,
ranging from brown dwarf searches to IR quasar variability studies. As
additional years of NEOWISER data become publicly available, it will be 
necessary to continue updating the full-depth AllWISE+NEOWISER coadds to 
maximize the achieved W1/W2 depths. Finally, the creation of WISE-only (as 
opposed to forced photometry) catalogs based on deep coadds which incorporate
NEOWISER images will be needed to enable a variety of exciting discoveries.

>>>>

Although the present analysis constituted a significant data processing 
endeavor, it represents only a small fraction of the work that must
be done to maximize science return from the NEOWISER imaging data set.
Creation of time-resolved coadds spanning the $\sim$5 year AllWISE-NEOWISER
time baseline would enable a wealth of important time-domain projects,
ranging from brown dwarf searches to infrared quasar variability studies. As
additional years of NEOWISER data become publicly available, it will be 
necessary to continue updating the full-depth AllWISE+NEOWISER coadds to 
maximize the achieved W1/W2 depths. Finally, the creation of WISE-only (as 
opposed to forced photometry) catalogs based on deep coadds which incorporate
NEOWISER images will be needed to enable a variety of exciting discoveries.
